Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-14 MDPI/response_letter.tex

\end{letter}

% modify the page to use the space more efficiently
\addtolength{\textwidth}{1.5cm}
\addtolength{\textheight}{2.0cm}

\textbf{Reviewer 1}
\textit{}

\begin{enumerate}
\item \textit{The main findings of your results should be highlighted in abstract} 
We have rewritten the abstract. The abstract now contains main findings of our paper.

@@

\item \textit{How do you think control factors in open system such as pressure and temperature}

\end{enumerate}

\textbf{Reviewer 2}
\textit{This manuscript is about creating a new model the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous solution.}
\begin{enumerate}

\item \textit{Abstract needs to re-write as and please follow the IMRAD instruction.}
We have rewritten the abstract. We believe that the abstract is much more attractive now.
\item \textit{There is introduction in the abstract, however, it needs to write more about the aim of this work, method, result and conclusion.}
We have rewritten the abstract according to your advice.
\item \textit{Avoid to use word 'we' in the abstract as well as manuscript.}
Corrected.
\item \textit{line 247 in what table?}
We meant Table 1. Corrected.
\item \textit{Where is the method of this work?} 
The method idea is outlined in the paragraph "Physics behind the desalination process" and described in the section "Theory behind the simulation". We did not want to bother the readers too much with technical aspects of the smulations, so technical details are in ESI.
\item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
We improved the writing style of the manuscript and corrected the grammatical errors.
\item \textit{Please explain more detail about the process, how the process run and how the data could be explained and become more interesting for reader.}

@@

\end{enumerate}

\textbf{Reviewer 3}

\textit{}
\begin{enumerate}
\item \textit{The full stop in the title should be revised.}
Noted. Revised.
\item \textit{The abstract needs to be revised and be more attractive. The research gap, novelty and main findings should be concisely mentioned in the abstract.}
We have rewritten the abstract. We believe that the abstract is much more attractive now.
\item \textit{In this current shape, the manuscript looks like a report. The authors have to revise the flow of the context to attract the readers.}
We have revised and changed the manuscript to be more attractive for the readers. 
\item \textit{The manuscript must be improved by checking once again in English and technical writing. }
We improved the writing style of the manuscript and corrected the grammatical errors.

### 2022-09-14 gibbs.tex

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Recently, polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
On the other hand, the insoluble cross-linked hydrogel network enables dewatering under the influence of external (thermal and/or mechanical) stimulus.
Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane.
These above mentioned hydrogel properties designates them as excellent candidates for desalination, and, at the same time, avoid the use of expensive membranes.
In this article, we present our recent theoretical study of polyelectrolyte hydrogel usage for water desalination. 
Employing coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting gel phase and supernate aqueous salt solution phase.
We performed a sequence of step-by-step hydrogel compressions in \emph{open} and \emph{closed} systems.
The compression in \emph{open system} causes the decrease of salt ions inside the hydrogel,
while the compression in \emph{clesed system} causes the decrease of the salt concentration in the supernatant solution.
We modeled this stepwise process of continuous decrease of water salinity from seawater up to freshwater concentrations.
We estimated the energy costs of the entire process as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.
}

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Recently, polyelectrolyte hydrogels have been proposed as draw agents for the forward osmosis desalination techniques. 
Indeed, polyelectrolyte hydrogels have the ability to absorb a big amount of water across an osmosis membrane as a result of their swelling pressure. 
On the other hand, the insoluble cross-linked hydrogel network enables dewatering under the influence of external (thermal and/or mechanical) stimulus.
Moreover, from a thermodynamic perspective, the polyelectrolyte hydrogel is already an osmotic membrane.
These above mentioned hydrogel properties designates them as excellent candidates for desalination, and, at the same time, avoid the use of expensive membranes.
In this article, we present our recent theoretical study of polyelectrolyte hydrogel usage for water desalination. 
Employing coarse-grained model and the Gibbs ensemble, we modeled the thermodynamic equilibrium between coexisting gel phase and supernate aqueous salt solution phase.
We performed a sequence of step-by-step hydrogel compressions in \emph{open} and \emph{closed} systems.
The compression in \emph{open system} causes the decrease of salt ions inside the hydrogel,
while the compression in \emph{closed system} causes the decrease of the salt concentration in the supernatant solution.
We modeled this stepwise process of continuous decrease of water salinity from seawater up to freshwater concentrations.
We estimated the energy costs of the entire process as 38.2 J per production of 1 liter of potable water, which is comparable with reverse osmosis.
}
